Title of the Master Thesis

### 2015-10-01 Master Thesis/thesis.tex
Add synopsis
Print index
Pop introduction
Pop bibliography
Add tikz-babel package
Add steps
Fix declaration

\documentclass[11pt,a4paper,openany]{memoir}
\usepackage{fontspec}
\usepackage[english]{babel}
\usepackage{amsmath, amsfonts, amssymb, amsthm}
\usepackage{paralist}
\usepackage{tikz-cd}
\linespread{1.1}
\usepackage{hyperref}
\hypersetup{
	bookmarksopen=true,
	pdfstartview=FitH
}
\usepackage[inner=4cm,outer=3cm,top=3cm,bottom=3cm]{geometry}
\author{Yichuan Shen}
\title{Title of the Master Thesis}
\makeindex

@@

\theoremstyle{plain}
\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\newtheorem*{example}{Example}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

@@

\vspace*{0cm}
\vfill
\paragraph{Declaration.} I declare that I carried out this master thesis independently, and only with the cited sources, literature and other professional sources. The master thesis was not used in the same or in a similar version to achieve an academic grading or is being published elsewhere.\\
\vspace{7mm}\\
\rule{7cm}{0.4pt}
\clearpage

@@

\mainmatter
\pagenumbering{arabic} 
\setcounter{page}{5}
\tableofcontents

\chapter{Introduction}

\clearpage

\section{Notation}

$\begin{array}{ll}
\mathbb{N} & \text{Natural numbers} \\
\mathbb{Z} & \text{Integers}\\
\mathbb{Q} & \text{Rational numbers}\\
\mathbb{R} & \text{Real numbers}\\
\mathbb{C} & \text{Complex numbers}\\
\mathbb{Z}_p & \text{$p$-adic integers}\\
\mathbb{Q}_p & \text{$p$-adic numbers}
\end{array}$

\chapter{First chapter}

\begin{thebibliography}{99999999}

\bibitem[DDMS99]{DDMS99}
	J. D. Dixon, M. P. F. du Sautoy, A. Mann, D. Segal (1999)
	\textit{Analytic Pro-$p$ Groups}.
	Cambridge Studies in Advanced Mathematics,
	2nd Edition.

\end{thebibliography}

%\printindex
\end{document}

>>>>

\documentclass[11pt, a4paper, openany]{memoir}
\usepackage{fontspec}
\usepackage[english]{babel}
\usepackage{amsmath, amsfonts, amssymb, amsthm}
\usepackage{paralist, tikz}
\usetikzlibrary{cd, babel}
\usepackage[inner=4cm, outer=3cm, top=3cm, bottom=3cm]{geometry}
\usepackage{hyperref}
\hypersetup{bookmarksopen=true, pdfstartview=FitH}
\linespread{1.1}
\author{Yichuan Shen}
\title{Title of the Master Thesis}
\makeindex

@@

\theoremstyle{plain}
\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\newtheorem*{example}{Example}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem{step}{Step}

@@

\vspace*{0cm}
\vfill
\paragraph{Declaration.} I declare that I carried out this master thesis independently, and only with the cited sources, literature and other professional sources. This thesis was not used in the same or in a similar version to achieve an academic grading or is being published elsewhere.\\
\vspace{7mm}\\
\rule{7cm}{0.4pt}
\clearpage

@@

\pagenumbering{arabic}
\setcounter{page}{5}
\tableofcontents

\input{introduction.tex}

\mainmatter
\setcounter{page}{9}

\input{synopsis.tex}
\input{bibliography.tex}

\printindex
\end{document}
